---
output:
  rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# hierBipartite

[![CRAN](https://www.r-pkg.org/badges/version/hierBipartite)](https://www.r-pkg.org/pkg/hierBipartite)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/hierBipartite)](https://CRAN.R-project.org/package=hierBipartite)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![MIT license](http://img.shields.io/badge/license-MIT-brightgreen.svg)](https://opensource.org/licenses/MIT)

> Bipartite Graph-based Hierarchical Clustering

__Author:__ [Calvin Chi](https://calvintchi.github.io/)

---

## About

Bipartite graph-based hierarchical clustering performs hierarchical 
clustering of groups of samples based on association patterns between two 
sets of variables. It is developed for pharmacogenomic datasets and datasets 
sharing the same data structure. In the context of pharmacogenomic datasets, 
the samples are cell lines, and the two sets of variables are typically 
expression levels and drug sensitivity values. For this method, sparse 
canonical correlation analysis from Lee, W., Lee, D., Lee, Y. and 
Pawitan, Y. (2011) <doi:10.2202/1544-6115.1638> is first applied to extract 
association patterns for each group of samples. Then, a nuclear norm-based 
dissimilarity measure is used to construct a dissimilarity matrix between 
groups based on the extracted associations. Finally, hierarchical clustering 
is applied.

---

## Installation

For standard use, we recommend installing the package from
[CRAN](https://CRAN.R-project.org/package=hierBipartite) via

```{r cran-installation, eval = FALSE}
install.packages("hierBipartite")
```

---

## Example

Minimially sufficient example of using `hierBipartite`. Please refer to the
[vignette](https://cran.r-project.org/web/packages/hierBipartite/vignettes/hierBipartite.html)
for detailed usage.

```{r example, message=FALSE, warning=FALSE, eval=FALSE}
library(hierBipartite)
data(ctrp2)

groups = ctrp2$groups
X = ctrp2$X
Y = ctrp2$Y

result = hierBipartite(X, Y, groups)
```
